\documentclass{resume2}

\usepackage[left=0.45in,top=0.3in,right=0.45in,bottom=0.3in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\linespread{0.93}

\name{Kismat Kunwar}
\contact{
  West Haven, CT \quad|\quad
  \href{mailto:kismatkunwar89@gmail.com}{kismatkunwar89@gmail.com} \quad|\quad
  \href{https://linkedin.com/in/kunwarkismat}{linkedin.com/in/kunwarkismat} \quad|\quad
  \href{https://kismatkunwar89.github.io/portfolio/}{Portfolio}
}

\begin{document}
\makeheader

%                -
% SUMMARY
%                -
\section{Summary}
Cybersecurity graduate student with hands-on incident response and digital forensics experience. Published researcher at ICDF2C on applying LLMs to structured representation and mapping of forensic artifacts into CASE/UCO knowledge graphs. Investigated real phishing and ransomware precursor incidents using CrowdStrike EDR. Proficient in Python/Bash; strong communicator with experience presenting findings to technical and non-technical audiences.

%                -
% EDUCATION
%                -
\section{Education}

\textbf{Master's in Cyber Security} (GPA: 3.9) \hfill Aug 2024 -- Present\\
University of New Haven, West Haven, CT

\medskip
\textbf{Bachelor's in Cyber Security, First Class Honors} (GPA: 3.96) \hfill May 2020 -- Jun 2023\\
Coventry University, UK

%                -
% SKILLS
%                -
\section{Skills}

\textbf{Proficient with:} CrowdStrike Falcon EDR, SIEM (ELK), incident response (NIST SP 800-61, NIST CSF), threat intelligence (MITRE ATT\&CK, D3FEND, STIX/TAXII, Cyber Kill Chain, IOC analysis), network defense (Wireshark, tcpdump, Suricata, Snort), DFIR (Autopsy, EZ Tools, CASE/UCO), Python, Bash

\smallskip
\textbf{Familiar with:} Malware analysis, memory forensics, AI coding tools (Claude Code, Codex), Splunk, Sentinel, OSINT (Maltego, VirusTotal, OTX), Azure, AWS, penetration testing (Kali Linux, Metasploit, Burp Suite)

\smallskip
\textbf{Certifications:} (ISC)\textsuperscript{2} CC \textbullet{} Cisco CCNA \textbullet{} Microsoft Azure Fundamentals (AZ-900) \quad \textbf{CTF:} NCAE CyberGames (forensics, web exploitation, network analysis)

%                -
% EXPERIENCE
%                -
\section{Experience}

\textbf{Provost Research Assistant} \hfill Sep 2024 -- Present\\
\textit{Tagliatela College of Engineering, University of New Haven, West Haven, CT}
\begin{itemize}[leftmargin=1.2em,itemsep=-2pt,topsep=2pt]
  \item Engineered LLM pipelines (GPT-4/DeepSeek/Gemini) to parse unstructured forensic evidence and produce CASE/UCO-compliant knowledge-graph-ready output, cutting manual processing $\sim$30\%.
  \item Built the Indicator of Inconsistency (IoI) Framework, an ontology-driven SPARQL rule library detecting cross-artifact contradictions across MFT, USN journal, event logs, LNK files, and Office metadata; validated against 87M+ RDF triples across 5 antiforensic test cases.
  \item Presented first-author research at ICDF2C on LLM-driven DFIR artifact mapping; delivered findings to academic and practitioner audiences.
\end{itemize}

\medskip
\textbf{Security Support Analyst} \hfill May 2023 -- Mar 2024\\
\textit{Raechal Enterprise Pvt Ltd, Kathmandu, Nepal}
\begin{itemize}[leftmargin=1.2em,itemsep=-2pt,topsep=2pt]
  \item Investigated a credential-harvesting phishing campaign flagged across 3 endpoints; correlated spoofed sender domains, macro-enabled attachment hashes, and O365 login anomalies to confirm compromise; delivered full incident report to senior engineers within 4 hours.
  \item Triaged a ransomware precursor alert by identifying lateral SMB enumeration and abnormal PowerShell execution on a finance workstation; escalated with IOCs, attack timeline, and containment recommendation before encryption stage was reached.
  \item Managed $\sim$15 weekly EDR/MFA tickets; tuned Falcon EDR detection policies to reduce false positives, verified endpoint patch compliance, and coordinated change control requests with engineering teams.
\end{itemize}

%                -
% PROJECTS
%                -
\section{Projects}

\textbf{Flamingo Neck Networks Internal Pentest} \hfill Course Lab\\
Conducted full-scope internal assessment (10.248.1.0/24): exploited default PostgreSQL credentials for RCE, leveraged guest-to-admin misconfiguration to execute Pass-the-Hash, achieving full AD domain compromise. Documented 9 findings (2 Critical) with CVSS scores, attack chain narrative, and prioritized remediation guidance.

\medskip
\textbf{Threat Intelligence Platform} \hfill In Progress\\
Flask app aggregating AbuseIPDB, OTX, VirusTotal, and GreyNoise feeds with automated risk scoring, MITRE ATT\&CK mapping, and export to PDF/CSV/JSON for analyst reporting workflows.

\medskip
\textbf{Malware Research and Development.} APT evasion research using C2 frameworks; studied obfuscation, detection bypass, and persistence techniques to inform defensive detection engineering.

\medskip
\textbf{VectorProbe} (In Progress). Python tool chaining Nmap, Searchsploit, and enum4linux-ng for automated service discovery, vulnerability correlation, and Markdown reporting.

\end{document}
